Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM

### 2018-10-09 doc/issre2018/introduction.tex
Changed git ignore and removed some clutter

The problem of test data generation has been actively studied for the past three decades. In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\mbox{\emph{JSContest}}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}). Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints. However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reaches about 50\% \emph{branch coverage} on the selected subjects. At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications. But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach. In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. We summarize our contributions as follows:
\begin{enumerate}[leftmargin=5mm]
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input (including \emph{tags} and \emph{attributes}), which is syntactically valid and compliant with the recent HTML5 specification.
\item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target. In contrast to the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly achievable.
\item Based on the case studies found in two related papers~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results. The validation shows the effectiveness of the framework in covering target branches with a reasonable efficiency. Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.
\end{enumerate}

>>>>

The problem of test data generation has been actively studied for the past three decades. In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\mbox{\emph{JSContest}}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}). Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints. However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reaches about 50\% \emph{branch coverage} on the selected subjects. At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications. But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach. In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}~\cite{jedi}. We summarize our contributions as follows:
\begin{enumerate}[leftmargin=5mm]
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input (including \emph{tags} and \emph{attributes}), which is syntactically valid and compliant with the recent HTML5 specification.
\item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target. In contrast to the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly achievable.
\item Based on the case studies found in two related papers~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results. The validation shows the effectiveness of the framework in covering target branches with a reasonable efficiency. Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.
\end{enumerate}
